The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-07-25 paper/ms.tex
abundance study initial draft done

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element. From this observing run we have 35 unique targets with seismic \logg and spectra.

\textcolor{red}{Keith - can you describe in more detail how you got the abundances here?}

>>>>

For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element. We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments at higher resolution and SNR. From this observing run we have 35 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
